# Accept/Reject Algorithm

## 201530175 È²¼ºÀ± 

## Generating random numbers from standard normal distribution
## using Accept/Reject Algorithm

### Find value M and target(Y ~ N(0,1)) and candidate(V ~ f(v))
### U ~ Uniform(0,1)
### (a) : V ~ Cauchy(0,1), (b) : V ~ Double Exponential(0,1)

## Accept/Reject Algorithm

### Let Y~fy and V~fv, where fy and fv have common support with M such that
### M=sup(fy(y)/fv(y))

### To generate a random variable Y~fy :
### a. Generate U~Uniform(0,1), V~fv, independent.
### b. If U<(1/M)*(fy(V)/fv(V)), set Y=V. Otherwise, return to step(a).


## (a) Cauchy distribution

###1 Find M
```{r}
y1 <- seq(-1000,1000,by=0.001)
grid.m1 <- dnorm(y1,0,1)/dcauchy(y1,0,1)
(M1 <- grid.m1[which.max(grid.m1)])
```

###2 Accept/Reject Algorithm
```{r}
u1 <- runif(length(y1),0,1) ; v1 <- rcauchy(length(y1),0,1)
condition1 <- dnorm(v1,0,1)/(M1*dcauchy(v1,0,1))
select.y1 <- ifelse(u1 < condition1,TRUE,FALSE)
```

## (b) Double Exponential distribution

### Install packages for generating random numbers from
### Double Exponential distribution
```{r}
library(smoothmest)
```

###1 Find M
```{r}
y2 <- seq(-1000,1000,by=0.001)
grid.m2 <- dnorm(y2,0,1)/ddoublex(y2,0,1)
(M2 <- grid.m2[which.max(grid.m2)])
```

###2 Accept/Reject Algorithm
```{r}
u2 <- runif(length(y2),0,1) ; v2 <- rdoublex(length(y2),0,1)
condition2 <- dnorm(v2,0,1)/(M2*ddoublex(v2,0,1))
select.y2 <- ifelse(u2 < condition2,TRUE,FALSE)
```

## (c) Compare two results

### Drawing histograms for compare

### (1) Candidate is Cauchy(0,1)
```{r}
random.y1 <- v1[select.y1] 
hist(random.y1,prob=TRUE,nclass=20,
     main="Accept/Reject Algorithm Y~N(0,1),V~Cauchy(0,1)",col="green")
lines(y1,dnorm(y1,0,1),col="red",lwd=2)
```

### (2) Candidate is Double Exponential(0,1)
```{r}
random.y2 <- v2[select.y2] 
hist(random.y2,prob=TRUE,nclass=20,
     main="Accept/Reject Algorithm Y~N(0,1),V~Double Exponential(0,1)",col="yellow")
lines(y2,dnorm(y2,0,1),col="blue",lwd=2)
```

### Calculate mean and variance
```{r}
print(list(mean(random.y1),abs(mean(random.y1)-0),sd(random.y1)))
print(list(mean(random.y2),abs(mean(random.y2)-0),sd(random.y2)))
```

